Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.

### 2018-11-30 paper/snakemajoranas.tex
Add tikz file for system
Uncomment wavefunction figure
Added hamiltonian
fix notation
Add small piece of physical picture text
Added a bunch of text to the manuscript

\DeclareMathOperator{\e}{e}
\DeclareMathOperator{\de}{d\!}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Pf}{Pf}
\DeclareMathOperator{\Det}{Det}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\re}{Re}

@@

\begin{figure}[!htb]
% \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
\caption{Setups. Figure of a straight and zigzag system, including trajectories.
\label{fig:setup}}
\end{figure}

@@

\begin{align}
    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
\end{align}
\begin{footnotesize}
\begin{align}
    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\left(\mu_s\right) - k_x^2 \right]^\frac{1}{2}\\
    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
\end{align}
\end{footnotesize}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Calculating the bandstuctures
%%██████████████████████████████████████████████████████████████████████████
\section{Calculating the bandstuctures.}

%%██████████████████████████████████████████████████████████████████████████
%%██ Calculating the topological phase diagram
%%██████████████████████████████████████████████████████████████████████████
\section{Calculating the topological phase diagram.}

\comment{We use a generalized eigenvalue problem to find all phase boundaries at once.}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Localization lengths and shape effect
%%██████████████████████████████████████████████████████████████████████████
\section{Localization lengths and shape effect}

\comment{We find the Majorana lengths by calculating the slowest decaying mode.}

\begin{figure}[!htb]
% \includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
\caption{Wavefunctions for different sizes and geometries.
With (a) a straight system, (b) a zigzag sytem, (c) a system where the normal region is defined by two parallel sine waves, and (d) a system with the Laeven shape.
Inside the figure we indicate the Majorana lenght (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
\label{fig:wavefunctions}}
\end{figure}

>>>>

\DeclareMathOperator{\e}{e}
\DeclareMathOperator{\de}{d\!}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Pf}{Pf}
\DeclareMathOperator{\Det}{Det}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\re}{Re}
\newcommand{\kx}{k_x}
\newcommand{\ky}{k_y}
\newcommand{\meff}{m_\text{eff}}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Physical picture
%%██████████████████████████████████████████████████████████████████████████
\section{Physical picture}
We consider a system [\ref{fig:setup}] consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
A magnetic field pointed along the x direction is applied.
We model the system with a BdG hamiltonian; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
For the zigzag geometry, we take a sawtooth like pattern wher $z_x$ is periodicity, $z_y$ the amplitude and W the width of the junction.
\begin{small}
\begin{align}
    H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right)\tau_z+
        E_\text{z} \sigma_z+
        \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +
        \Delta \tau_y
\end{align}
\label{eq:hamiltonian}
\end{small}

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/systemPicture.pdf}
\caption{Setups. Figure of a straight and zigzag system, including trajectories.
\label{fig:setup}}
\end{figure}

@@

\begin{align}
    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
\end{align}
\begin{footnotesize}
\begin{align}
    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\left(\mu_s\right) - k_x^2 \right]^\frac{1}{2}\\
    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
\end{align}
\end{footnotesize}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Calculating the bandstuctures
%%██████████████████████████████████████████████████████████████████████████
\section{Calculating the bandstuctures.}
In figure \ref{fig:bandstuctures}, We calculate the bandstructure for a zigzag system with varying amplitude using Kwant.
As the zigzag introduces super cell, we see a folded bandstructure.
For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased tenfolds.
We claim this effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced. This has an effect on the Majorana coherence length, as described later on in the manuscript.

%%██████████████████████████████████████████████████████████████████████████
%%██ Calculating the topological phase diagram
%%██████████████████████████████████████████████████████████████████████████
\section{Calculating the topological phase diagram.}
In order to create a topological phase diagram we would normally compute the topolical invariant(pfaffian).
For a ribbon this is possible, but computing the invariant of the supercell is too computationally expensive.
Using a generalized eigenvalue problem also proved unsuccesful due to numerical errors, so we resort to simply calculating the gap and noting the gap closings.

Similar to what is described in Pientka et. al [\cite{pientka2017topological}], we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean toplogical region.
\comment{We use a generalized eigenvalue problem to find all phase boundaries at once.}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Localization lengths and shape effect
%%██████████████████████████████████████████████████████████████████████████
\section{Localization lengths and shape effect}
Using the tight-binding package kwant, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinosoids.
We then superimpose them onto the geometry, as in figure \ref{fig:wavefunctions}.
For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
All of the zigzag type geometries however show greatly reduced coherence length.\tabularnewline
This can be explained by two effects: the increase in topological gap, but also the beforementioned reduction of the group velocity.
\comment{We find the Majorana lengths by calculating the slowest decaying mode.}

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
\caption{Wavefunctions for different sizes and geometries.
With (a) a straight system, (b) a zigzag sytem, (c) a system where the normal region is defined by two parallel sine waves, and (d) a system with the Laeven shape.
Inside the figure we indicate the Majorana lenght (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
\label{fig:wavefunctions}}
\end{figure}
